Best Practices for Developing Monte Carlo Methodologies in Molecular Simulations [Article v\versionnumber]

### 2025-06-16 paper/paperv1.0.tex
Key figure and ref to orientation changes

Thus, the acceptance probability for deletions is given by
\begin{equation}
\chi = \frac{P_{\omega o} N_i}{Vz_i}e^{-\beta\Delta U},
\label{eq:lhs_del}
\end{equation}
where $P_{\omega o}=1$ (or incorporated into the definition of $z_i$) if rigid bodies are inserted with random orientations, or otherwise related to the Rosenbluth factor in CB \cite{frenkel_understanding_2002}.
Code Block~\ref{sim:ideal_gas_muvt} uses Eqs.~\ref{eq:lhs_ins} and \ref{eq:lhs_del} for an ideal gas to compare against theory, Eq.~\ref{eq:gce_ideal_gas_density}.

>>>>

Thus, the acceptance probability for deletions is given by
\begin{equation}
\chi = \frac{P_{\omega o} N_i}{Vz_i}e^{-\beta\Delta U},
\label{eq:lhs_del}
\end{equation}
where $P_{\omega o}=1$ (or incorporated into the definition of $z_i$) if rigid bodies are inserted with random orientations (using quaternsions, as discussed in Section~\ref{sec:lhs_rotation} and \ref{sec:unit_sphere}), or otherwise related to the Rosenbluth factor in CB \cite{frenkel_understanding_2002}.
Code Block~\ref{sim:ideal_gas_muvt} uses Eqs.~\ref{eq:lhs_ins} and \ref{eq:lhs_del} for an ideal gas to compare against theory, Eq.~\ref{eq:gce_ideal_gas_density}.
